---
title: "Analyzing Restaurant Customer Review Using Sentiment Analysis"
author: "Piangkwan Jaikaew"
date: "17-12-2022"
output: pdf_document
---

```{r  Uno , echo=FALSE, message=FALSE, error= FALSE}

library(tidyverse)
library(syuzhet)
library(tidytext)
library(dplyr)
library(janeaustenr)
library(textdata)
```


# 1. Introduction

Customer satisfaction in the restaurant industry has an outsized impact on success. Asking for feedback and review helps in improving the customer satisfaction. The reviews plays a vital role for restaurants to be successful and steadily grow in the future.

In this case study, I will conduct a sentiment analysis for the local restaurant. The original dataset was sourced from Kaggle datasets. It consists of 1000 reviews from customers.

# 2. Summary

The dataset demonstrates mainly positive reviews, approximately 50% from word counts.By using three different sentiment analysis methods, NRC, bing and loughran to extract and analyze in text mining, it shown the correlated result as a positive feedback.

# 3. Methodology 
1. Clean and transform data using dplyr package.
2. Analyse sentiments using the syuzhet package based on the NRC sentiment dictionary.
3. Conduct sentiment analysis using the "bing" lexicon.
4. Conduct sentiment analysis using the "loughran" lexicon.
5. Visualization with ggplot2 package.


## Import and transform data.
```{r  , echo=FALSE, message=FALSE, warning=FALSE }
# import  datasets
df_res <- read_csv("C:/Users/mayjaikaew/Downloads/Restaurant_Reviews.csv")
#transform to tibble
text.res <- tibble(text = str_to_lower(df_res$Review))

```

## Sentiment Analysis

### Syuzhet package is used for sentiment analysis 

```{r echo=FALSE, message=FALSE, warning=FALSE}

# analyze sentiments using the syuzhet package based on the NRC sentiment dictionary
emotion.res <- get_nrc_sentiment(text.res$text)
#summarize each sentiments
emores_sum <- colSums(emotion.res)
#transform to data frame
df.emo <- data.frame(count=emores_sum, emotion=names(emores_sum))


# Data transformation
df.emo.pie <- df.emo %>% arrange(desc(count)) %>% 
  mutate(perc = `count` / sum(`count`)) %>% 
  arrange(perc) %>% mutate(labels = scales::percent(perc))
tib.emo.pie <- as_tibble(df.emo.pie)
tib.emo.pie
```

**Chart 1:** The table shows a number of count and percentage of ten different emotion categories. 

```{r  DataCharge2 , echo=FALSE, message=FALSE}
ggplot(df.emo.pie, aes(x = 2, y = perc, fill = emotion)) +
  geom_col( width=1, color="white") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5))+
  coord_polar("y", start=0) +
  theme_void() +
  labs(fill = "Emotion status", title = "Restaurant Review showing the percentage for ten emotion status ")+
  xlim(0.5, 2.5)

```

**Chart 2:** Approximately 50% of reviews expresses positive feeling toward the restaurant.

```{r  DataCharge3 , echo=FALSE, message=FALSE}
# create a barplot showing the counts for each of eight different emotions and positive/negative rating
ggplot(df.emo, aes(x = reorder(emotion, -count), y = count, fill = emotion)) + 
  geom_bar(stat = 'identity') +labs(title = "Distribution of emotion status from customer reviews.", x ="Sentiment")

```

**Chart 3:**  The word counts show mainly positive which is good news for restaurant.

### Sentiment Analysis with Bing lexicon

```{r  DataCharge4 , echo=FALSE, message=FALSE}
# sentiment analysis with the tidytext package using the "bing" lexicon
word_count <- text.res %>% unnest_tokens(output = word, input = text) %>%
  inner_join(get_sentiments("bing")) %>% count(word,sentiment, sort = TRUE)


# select top 10 words by sentiment
top_10_words <- word_count %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n, n = 10) %>% 
  ungroup() %>% 
  mutate(word = reorder(word, n)) 
top_10_words

# create a barplot showing contribution of words to sentiment
top_10_words %>% 
  ggplot(aes(word, n, fill = sentiment)) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~sentiment, scales = "free_y") + 
  labs(y = "Contribution to sentiment", x = NULL) + 
  coord_flip() 


```

**Chart 4:** The positive sentiment is demonstrated in a greater proportion than negative sentiment from bing lexicon.

### Sentiment Analysis with Loughran lexicon

```{r  DataCharge5, echo=FALSE, message=FALSE}
# sentiment analysis with the tidytext package using the "loughran" lexicon
loughran_counts <- text.res %>% unnest_tokens(output = word, input = text) %>%
  inner_join(get_sentiments("loughran")) %>%
  count(word, sentiment, sort = TRUE) 

# select top 10 words by sentiment
loughran_top_10_words <- loughran_counts %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n))
loughran_top_10_words

# create a barplot showing contribution of words to sentiment
loughran_top_10_words %>% 
  ggplot(aes(word, n, fill = sentiment)) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~sentiment, scales = "free_y") + 
  labs(y = "Contribution to sentiment", x = NULL) + 
  coord_flip() 

```

**Chart 5:** Still show primary positive! even more specific expressions such as uncertainty are shown by Loughran lexicon.

# 4. Conclusion

For limitation, the current data needs to provide a more oversized data frame and a specific period of time to measure on exact feedback in order to minimize a bias information to be as low as possible. \

